%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

\documentclass{beamer}

\mode<presentation> {
	\usetheme{Madrid}

	%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
	%\setbeamertemplate{footline}[page number] % To replace the footer line in all slides with a simple slide count uncomment this line
	
	%\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
	
	%\addtobeamertemplate{frametitle}{}{\section{\insertframetitle}} % To add all frame title into table of contents automacitally
	
	%\setbeamertemplate{items}[square]
}

\usepackage{graphicx}
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[DragonFly]{DragonFly - Surveil Transport sector into Smart City}
%\title[Traffic Policing]{ Intelligent Policing of Traffic}
\author[Group1]{
	{\small \textit{Guided by:}} Dr. Rafeeque P.C \\
	\medskip
	{\small \textbf{\textit{Group 1}}} \\
	Abhinand C \\
	Edwin Jose George \\
	Lavanya E.V \\
	Shilpa Suresh
}
\institute[GCEK]{Government College of Engineering Kannur}
\date{\today}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Contents}
\tableofcontents
\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------

%------------------------------------------------
\section{Problem Statement}
\begin{frame}
	\frametitle{Problem Statement}
	To provide a facility to track public vehicles, see their trip status and monitor their path. Also provide facility to track vehicles, detect accidents using image processing to provide safe public transport system. 
\end{frame}

%------------------------------------------------
\section{Motivation and Relevance}
\begin{frame}
	\frametitle{Motivation and Relevance}
	\begin{enumerate}
		\item Enable tracking of vehicles, ie, retrieving route history by typing in the description
		\item Alert Control Room, \& emergency services in case of accident
		\item Public APIs for location of public transport, and tracking system like Indian Railway NTES system
	\end{enumerate}
	
\end{frame}


%------------------------------------------------
\section{Proposed Framework}
\begin{frame}
	\frametitle{Proposed Framework}
	content goes here...
\end{frame}

%------------------------------------------------
\section{Requirements}
\begin{frame}
	\frametitle{Requirements}
	content goes here...
\end{frame}


%------------------------------------------------
\section{Challenges and issues}
\begin{frame}
	\frametitle{Challenges and issues}
	content goes here...
\end{frame}


%------------------------------------------------
\begin{frame}
	\Huge{\centerline{The End}}
\end{frame}

%-------------------------incomplete infos-----------------------------
\section{Temporary info}
\begin{frame}
	The below slides are not to be included during presentation! 
\end{frame}

\subsection{Ponder points}
\begin{frame}
	\Huge{\centerline{Ponder points}}
\end{frame}

\begin{frame}
	\frametitle{What does this project do?}
	\begin{enumerate}
		\item GPS tracking vehicles (Transport Bus, School Bus, Cargo trucks, Taxi etc) to determine its location
		\item Predict the route and estimated time of arrival. Also get a glimpes of other avalaible modes of transport from a particular point
		\item Making use of traffic cameras to identify vehicles and track their route, helping authorities to trackdown a specific vehicle.
		\item Analysis on data to determine traffic flow to measure aspects such as speed, registration of vehicles etc to ensure regulation of traffic rules
	\end{enumerate}
\end{frame}

\begin{frame}
	\frametitle{Application Domain}
	\begin{enumerate}
		\item Locating public transport buses, their schedule and route planings
		\item Educational and other firms to track and monitor their transport system.
		\item Tracking down corrupt drivers/vehicles \\(check on polution/insurance/registration-permits, tagging specifing vehicle etc)
		\item Enforcment of traffic rules. (Speed limits, helmets for 2 wheelers etc)
		\item Alerting the suggesting routes for emergency servies like ambulance, fire-force etc.
		\item Accident detection
	\end{enumerate}
\end{frame}

\begin{frame}
	\frametitle{Features}
	\begin{enumerate}
		\item Route tracking and planning
		\item Monitoring traffic rules using image processing
		\item Public APIs for locating units (Indian Railways)
		\item Identifying accidents and trigging associated events.
	\end{enumerate}
\end{frame}


\begin{frame}
	\frametitle{Limitation at sight?}
	\begin{enumerate}
		\item Real time image processing needs better hardware support.	
		\item How to detect accidents, where to deploy hardware units?
		\item Traffic cameras can effected from blind spots.
		\item Video capture difficulty
		\begin{itemize}
			\item Moving vehicles might give blurry image
			\item Envrionmental factors (rain, fog)
			\item Light beams of vehicles in night light can blind the camera
		\end{itemize}
		\item Scale up issues
		\begin{itemize}
			\item hardware processing limitation
			\item Addressing vast varity of vehicles (issue of smart cities)	
		\end{itemize}
		\item Legal considerations
	\end{enumerate}
\end{frame}
%----------------------------------------------------------------------------------------

\end{document} 