%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

\documentclass{beamer}

\mode<presentation> {
	\usetheme{Madrid}

	%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
	%\setbeamertemplate{footline}[page number] % To replace the footer line in all slides with a simple slide count uncomment this line
	
	%\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
	
	%\addtobeamertemplate{frametitle}{}{\section{\insertframetitle}} % To add all frame title into table of contents automacitally
	
	%\setbeamertemplate{items}[square]
}

\usepackage{graphicx}
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables


%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[DragonFly]{Project DragonFly \\ Surveil Transport sector into Smart City}
\author[Group 3]{
	{\small \textit{Guided by:}} Dr. Rafeeque P.C \\
	\medskip
	{\small \textbf{\textit{Group 3}}} \\
	Abhinand C \\
	Edwin Jose George \\
	Lavanya E.V \\
	Shilpa Suresh
}
\institute[GCEK]{Government College of Engineering Kannur}
\date{\today}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Contents}
\tableofcontents
\end{frame}

%########################################################################################
%	PRESENTATION SLIDES
%########################################################################################

\section{Introduction}
\begin{frame}{Introduction}
    Policing agencies have setup vast networks of distributed surveillance cameras along major routes. The sheer amount of data generated is overwhelming for manual analysis, to trace routes of rouge vehicles or optimally manage traffic, and in practicality the surveillance cameras serves just as an after event mechanism to verify. Significant amount of human resource would be required to utilize cameras as intended and even to alert accidents in real time. \\~\\

    The wide gap in human resource availability and the tedious effort required for traffic analysis, results in under utilization of surveillance infrastructure for policing and improper traffic management.    
\end{frame}


%########################################################################################

\section{Motivation}
\begin{frame}{Motivation}
	\begin{enumerate}
	    \item Public APIs for location of public transport, and tracking system (like Indian Railway NTES system) enlighten public with current traffic and its trends.
	    \item Provides facility to decide when, where, and which transport modes are available.
		\item Enable tracking of vehicles, ie, retrieving route history and related info by typing in the description helps authority in promoting quality flow of traffic.
		\item Aids policing agencies to track routes of rouge vehicles and automate surveillance footage analysis.
		\item Aids in better Alert Control System, \& emergency services in case of accidents and/or other events.		
	\end{enumerate}
\end{frame}

%########################################################################################

\section{Literature Review}
\begin{frame}{Literature Review}
\end{frame}

%########################################################################################

\section{Problem Statement}
\begin{frame}{Problem Statement}
	A novel approach to provide a highly integrated platform utilizing existing infrastructure to monitor public transport system, and extend timely information to both public and policing agencies, with intuitive interface.
\end{frame}

%########################################################################################

\section{Objective}
\begin{frame}{Objective}
\end{frame}

%########################################################################################

\section{Contributions Made}
\begin{frame}{Contributions Made}
\end{frame}

%########################################################################################

\section{Requirements}
\subsection{Functional Requirements}
\begin{frame}{Functional Requirements}
\end{frame}

\subsection{Non-functional Requirements}
\begin{frame}{Non-functional Requirements}
    \begin{itemize}
        \item To be used by non technical public - appealing and simple interface
        \item Provide reliable and consistent information and service
        \item Higher concerns on security of personal and public data.
        \item Must account for mobility and agility.
    \end{itemize}
    
    \begin{block}{Execution qualities}
        Good interpretation of data which results reasonable processing of information, considering security of processed data.
    \end{block}

    \begin{block}{Evolution qualities}
        Large volume of data needs to be interpreted and processed as clusters. Needs to account for scalability of resources and services, along with extension of new services.
    \end{block}
\end{frame}

%########################################################################################

\section{Proposed Framework}
\begin{frame}{Proposed Framework}
\end{frame}

%########################################################################################

\subsection{General Architecture/Methodology/ Frame Work/ Technology}
\begin{frame}{Architecture}
\end{frame}

\subsection{Detailed Design}
\begin{frame}{Detailed Design}
\end{frame}

\subsection{Dataset/Input}
\begin{frame}{Dataset}
\end{frame}

%########################################################################################

\section{Work done so far}
\begin{frame}{Work done so far}
\end{frame}

%########################################################################################

\section{Work planned}
\begin{frame}{Work Planned}
\end{frame}

%########################################################################################

\section{Conclusion}
\begin{frame}{Conclusion}
\end{frame}

%########################################################################################

\section{References}
\begin{frame}[allowframebreaks, noframenumbering]{References}
	\nocite{*}
	\bibliographystyle{IEEEtran}
	\bibliography{IEEEabrv,reference.bib}
\end{frame}

%########################################################################################

\end{document} 